Towards Language Model-based Identification of Business Clusters

### 2023-07-03 report/report.tex
grammarly is your friend

\begin{abstract}
	One of the most important decisions every business has to decide on a physical location. Identifying the right location is crucial for effective marketing strategies reaching the intended customer base, it can reduce transportation costs, and locating in a vibrant regional business clusters can have significant positive effects on business development.
	However, strategically acquiring \& analyzing data on regional economies, the corresponding companies along with their target market segments is very complex and labor-intensive.

	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites, into machine-readable data points and  applying clustering to make location recommendations for novel.

	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster related companies and categorize novel companies to a cluster.
\end{abstract}

@@

$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster from which a potential market segment can be inferred.

>>>>

\begin{abstract}
	One of the most important decisions every business has to decide on is a physical location. Identifying the right location is crucial for effective marketing strategies to reach the intended customer base. It can also reduce transportation costs, and locating in a vibrant regional business cluster can significantly positively affect business development.
	However, strategically acquiring \& analyzing data on regional economies, the affiliated companies, and their target market segments is very complex and labor-intensive.

	We propose to circumvent these challenges by leveraging state-of-the-art language models to transform publicly available company websites into machine-readable data points and applying clustering to make location recommendations for novel companies.

	A qualitative evaluation of our methods being applied to data from the German municipality Saarland demonstrates that our methods can accurately cluster related companies and categorize novel companies into existing clusters.
\end{abstract}

@@

$4)$ Lastly, we apply well-established clustering algorithms in the low-dimensional feature space to assign each company to a cluster from which a potential market segments can be inferred.
